\chapter{The tools : what tools will you use during the competition?}

\section{3D Modeling}

3D modeling is a fundamental tool essential for participation in the competition. It empowers you not only to conceive and design your ideal car but also to perform several crucial functions: \par
\begin{itemize}
    \item Verify the car's regulatory compliance by utilizing measurement tools within the 3D modeler.
    \item Generate technical drawings vital for regulatory submissions and manufacturing purposes. Many 3D modeling tools are equipped with the capability to produce these essential technical drawings, which are mandatory submissions for both national and world finals. Additionally, these drawings are indispensable when collaborating with manufacturers, as they often require precise technical specifications to produce parts accurately.
    \item Create compelling renderings of the car. Renderings play a significant role in the engineering process, not only as a required submission element but also for establishing and communicating the team's identity and branding.
\end{itemize}

The 3D modeling software most widely adopted throughout the competition is Autodesk's Fusion 360. This preference is attributed to several distinct advantages:

\begin{itemize}
    \item Fusion 360 encompasses all the aforementioned functionalities and tools necessary for success in the competition, providing a comprehensive suite for design, compliance checks, drawing generation, and rendering.
    \item A plethora of resources, both specifically tailored to the competition and generally applicable to 3D modeling, are available, offering opportunities to attain proficiency in the tool. 
    \item Fusion 360 is renowned for its intuitive interface, making it considerably more accessible and easier for beginners to navigate compared to many of its competitors. 
    \item Furthermore, a robust support network is readily available should you encounter any challenges. The online forums are highly responsive, and direct contacts within Autodesk are accessible for addressing specific questions or technical issues.
\end{itemize}

To acquire access to Fusion 360, please navigate to the following link: \href{https://www.autodesk.com/education/edu-software/overview}{https://www.autodesk.com/education/edu-software/overview}. Proceed by clicking on "student" and then follow the subsequent steps outlined on the website. For verification purposes, you can furnish any school-related documentation, such as report cards, enrollment documentation, or student identification cards. Once verified, you will be able to download and install the software, enabling you to commence your 3D modeling endeavors.

\section{Simulations}

For the competition, simulation tools are crucial for optimizing car performance and validating designs, significantly reducing the need for costly physical prototypes and accelerating the design refinement process. Autodesk Fusion 360, widely used for 3D modeling, provides integrated simulation capabilities directly within its environment, accessible through an educational license. This includes tools for stress analysis (Finite Element Analysis or FEA) to ensure structural integrity, and Computational Fluid Dynamics (CFD) for analyzing airflow patterns to minimize drag. Fusion 360's intuitive interface and comprehensive suite make it highly accessible for beginners, streamlining the transition from design to initial analysis. Beyond Autodesk, Ansys serves as the official global CFD simulation partner for the competition, offering free access to its industry-leading software and learning resources for participants. Within the Ansys suite, Ansys Discovery is highly recommended as the best CFD software for beginners due to its intuitive user experience, real-time feedback, and focus on rapid design exploration and qualitative solutions. It allows teams to quickly test different design iterations and get immediate feedback on aerodynamic performance. However, Ansys Discovery offers less precision and is not suitable for complex problems or when results need to be within a 5-10\% accuracy range. If greater precision is required, teams can transition to Ansys Fluent, which is a more advanced and comprehensive CFD solver designed for highly detailed and accurate simulations of complex fluid flows. While Fluent provides accurate quantitative results and is the "gold standard" for precision, it has a steeper learning curve due to its complex interface and advanced features, requiring more skill and experience to operate effectively. Although comprehensive documentation and online resources are available, mastering Fluent requires a more dedicated learning commitment compared to Discovery. Access to Ansys software for students can be obtained via the Ansys website. \par

You get access to all the Fusion simulation tools at the same time as Fusion 360. To get access to Ansys simulations, go here to download Ansys for students : \href{https://www.ansys.com/academic/students/ansys-student}{https://www.ansys.com/academic/students/ansys-student}
